### 2016-09-20 R/ITHIM.Rmd
Updates to ITHIM.Rmd
Still having problems with AgeClass 1 and HHS9 cycling referent group mean.

reformatData <- function(data){
foo <- matrix(unlist(data), nrow = 7, ncol = 2)
foo <- rbind( c(0.1, 0.1), foo)
dimnames(foo) <- list(paste0("ageClass",1:8), c("F","M"))
return(foo[,c("M","F")])
}

@@

)
})
saveRDS(NHTS.trips, file = "./data/NHTS.trips.rds")
saveRDS(NHTS.person, file = "./data/NHTS.person.rds")
```

```{r loadData, eval = FALSE, echo = FALSE}
NHTS.person <- readRDS(file = "./data/NHTS.person.rds")
NHTS.trips <- readRDS(file = "./data/NHTS.trips.rds")
```

@@

#### Compute Natioal Metro Average

@@

```{r count, eval = TRUE, echo = FALSE}
listOfLists <- lapply(split(NHTS, NHTS$HHS),function(x) lapply(split(x, x$SEX), function(x) split(x, x$AGE)))
counts <- lapply(listOfLists, function(x) lapply(x, function(x) lapply(x, countPeople)))
walkLength <- lapply(listOfLists, function(x) lapply(x, function(x) lapply( x, tripTime, mode = "walk")))
cycleLength <- lapply(listOfLists, function(x) lapply(x, function(x) lapply( x, tripTime, mode = "cycle")))
countMatrix <- lapply(counts, reformatData)
walkMatrix <- lapply(walkLength, reformatData)
cycleMatrix <- lapply(cycleLength, reformatData)
meanWalkList <- mapply(walkMatrix,   countMatrix, FUN = function(x,y) x/y*7, SIMPLIFY = FALSE)
meanCycleList <- mapply(cycleMatrix, countMatrix, FUN = function(x,y) x/y*7, SIMPLIFY = FALSE)
RwtList <- lapply( meanWalkList, function(x) ifelse(x == 0, 1e-4, x) )
RctList <- lapply( meanCycleList, function(x) ifelse(x == 0, 1e-4, x) )
RwtList <- lapply( RwtList, function(x) x/x[3,2] )
RctList <- lapply( RctList, function(x) x/x[3,2] )
muwtList <- lapply( meanWalkList, function(x) x[3,2] )
muctList <- lapply( meanCycleList, function(x) x[3,2] )
```

@@

```{r ITHIMObjs, eval = TRUE, fig.width = 8, fig.height = 5, echo = FALSE, warning = FALSE}
upper <- 8
length <- 100

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")

@@

ITHIM.national <- createITHIM(vision = "baseline", region = "national")
ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)

>>>>

reformatData <- function(data){
foo <- matrix(unlist(data), nrow = 7, ncol = 2)
foo <- rbind( c(0, 0), foo)
dimnames(foo) <- list(paste0("ageClass",1:8), c("F","M"))
return(foo[,c("M","F")])
}

@@

)
})

@@

#### Compute National Metro Average

@@

```{r count, eval = TRUE, echo = FALSE}
listOfLists <- lapply(split(NHTS, NHTS$HHS),function(x) lapply(split(x, x$SEX), function(x) split(x, x$AGE)))
counts <- lapply(listOfLists, function(x) lapply(x, function(x) lapply(x, countPeople)))
walkLength <- lapply(listOfLists, function(x) lapply(x, function(x) lapply( x, tripTime, mode = "walk")))
cycleLength <- lapply(listOfLists, function(x) lapply(x, function(x) lapply( x, tripTime, mode = "cycle")))
countMatrix <- lapply(counts, reformatData)
walkMatrix <- lapply(walkLength, reformatData)
cycleMatrix <- lapply(cycleLength, reformatData)
meanWalkList <- mapply(walkMatrix,   countMatrix, FUN = function(x,y) ifelse(y == 0, 0, x/y*7), SIMPLIFY = FALSE)
meanCycleList <- mapply(cycleMatrix, countMatrix, FUN = function(x,y) ifelse(y == 0, 0, x/y*7), SIMPLIFY = FALSE)

#RwtList <- lapply( , function(x) ifelse(x == 0, 0, x) )
#RctList <- lapply( , function(x) ifelse(x == 0, 0, x) )

zeroReferentCase <- function(x){
  if(x[3,2]==0){
    return(matrix(1e-3,nrow=nrow(x),ncol=ncol(x), dimnames = dimnames(x)))
  }else{
    return(ifelse(x==0, 1e-3, x/x[3,2]))    
  }
}

RwtList <- lapply( meanWalkList, zeroReferentCase)
RctList <- lapply( meanCycleList, zeroReferentCase)
muwtList <- lapply( meanWalkList, function(x) ifelse(x[3,2]==0,1e-3, x[3,2]))
muctList <- lapply( meanCycleList, function(x) ifelse(x[3,2]==0,1e-3, x[3,2]))
```

@@

```{r ITHIMObjs, eval = TRUE, fig.width = 8, fig.height = 5, echo = FALSE, warning = FALSE}
upper <- 10
length <- 100

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIMList[[HHS]], "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIMList[[HHS]], "cv", 3.0288)
ITHIM.default <- updateITHIM(ITHIMList[[HHS]], "pWalk", 0.85)

@@

ITHIM.national <- ITHIM.default
ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)
